SST_patterns

### 2019-09-25 SST_patterns.Rmd
Updated

### intensoty 
trends_intensity_func <- function(df){
  upwellmodel <- glm(SACTN_upwell_base$intensity_mean[SACTN_upwell_base$event_no] ~ seq(1:length(SACTN_upwell_base$intensity_mean[SACTN_upwell_base$event_no])), 
                     family = gaussian(link = "identity"))
  upwellmodel0 <- glm(SACTN_upwell_base$intensity_mean[SACTN_upwell_base$event_no] ~ 1, family = gaussian(link = "identity")) # intercept only
  dat2 <- data.frame(site = SACTN_upwell_base$site, upwelltrend = round(as.numeric(coef(upwellmodel)[2]*10),1),
                       upwellR2 = round(1-logLik(upwellmodel)/logLik(upwellmodel0),2), # McFadden's psesudo-R2
                       upwell.val = round(coef(summary(upwellmodel))[,4][2],2))
}

@@

OISST_anov <- anova_func(df = OISST_upwell_base)
OISST_anov
CMC_anov <- anova_func(df = CMC_upwell_base)
CMC_anov

SACTN_anov <- sites_aov <- aov(intensity_mean ~ site * lubridate::year(date_start) * duration, data = SACTN_upwell_base)
SACTN_anov
```

>>>>

### Intensity: Chnaged the family and link because of the negative values within the dataset 
trends_intensity_func <- function(df){
  upwellmodel <- glm(SACTN_upwell_base$intensity_mean[SACTN_upwell_base$event_no] ~ seq(1:length(SACTN_upwell_base$intensity_mean[SACTN_upwell_base$event_no])), 
                     family = gaussian(link = "identity"))
  upwellmodel0 <- glm(SACTN_upwell_base$intensity_mean[SACTN_upwell_base$event_no] ~ 1, family = gaussian(link = "identity")) # intercept only
  dat2 <- data.frame(site = SACTN_upwell_base$site, upwelltrend = round(as.numeric(coef(upwellmodel)[2]*10),1),
                       upwellR2 = round(1-logLik(upwellmodel)/logLik(upwellmodel0),2), # McFadden's psesudo-R2
                       upwell.val = round(coef(summary(upwellmodel))[,4][2],2))
}

@@

OISST_anov <- anova_func(df = OISST_upwell_base)
summary(OISST_anov)
CMC_anov <- anova_func(df = CMC_upwell_base)
summary(CMC_anov)

SACTN_anov <- sites_aov <- aov(intensity_mean ~ site * lubridate::year(date_start) * duration, data = SACTN_upwell_base)
summary(SACTN_anov)
```
